---
title: "p8105_hw1_WZ2591"
author: "Wenyu Zhang"
date: "9/25/2021"
output: github_document
---

```{r}
library(tidyverse)
```


# Problem 1

## Create a data frame comprised of different types of variables:
First, create a data frame comprised of:

1. a random sample of size 10 from a standard Normal distribution;
2. a logical vector indicating whether elements of the sample are greater than 0;
3. character vector of length 10;
4. a factor vector of length 10, with 3 different factor “levels”.
    
```{r}
#create a data_frame
  set.seed(1234)
  data_frame = tibble (
    vec_numeric = rnorm(10),
    vec_logical = vec_numeric > 0,
    vec_character = c("a", "b", "c", "d", "e", "my", "name", "is", "wenyu", "zhang"),
    vec_factor = factor(c("Medium", "High", "Medium", "Low", "Low", "Medium", "High", "High", "Low", "Medium"))
  )

#check the data_frame
  data_frame
```

## Calculate the mean of  each variable in dataframe
Now calculate the mean of each variable in the data frame. 

It can work to get the mean of the numeric vectors and the logical vectors. The mean function converts the logical vectors from "TRUE" and "FALSE" to 1 and 0, respectively, and calculates their arithmetic mean. Code and results are shown below.
```{r}
#the mean of the numeric vectors and the logical vector
  mean(pull(data_frame, vec_numeric))
  mean(pull(data_frame, vec_logical))
```
The mean value of vec_numeric is `r mean(pull(data_frame, vec_numeric))`, and the mean value of vec_logical is `r mean(pull(data_frame, vec_logical))`
```{r}
#the mean of the character vectors and the factor vector
  mean(pull(data_frame, vec_character))
  mean(pull(data_frame, vec_factor))
```
The mean value of vec_character and vec_factor are returned to NA, and a warning shows up. It is because mean function doesn't support these two types of variables.

## Apply the as.numeric function to the logical, character, and factor variables
```{r, eval = FALSE}
  as.numeric(pull(data_frame, vec_logical))
  as.numeric(pull(data_frame, vec_character))
  as.numeric(pull(data_frame, vec_factor))
```
After coercing the logical, character, and factor variables into type "numeric". 

Logical vectors "FALSE" and "TRUE" are turned into 0 and 1, respectively. Character variables are all returned to NA, and a warning shows up. Factor objects are turned to numbers showing their different levels. This help explain what happens when calculating the mean.

# Problem 2
## Describe the data in this dataset, including names / values of important variables

The name of data is "penguins" with 8 variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.


```{r}
  data("penguins", package = "palmerpenguins")
  names(penguins)
  skimr::skim(penguins)
```
The name of data is "penguins" with 8 variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year.

## Describe the size of data set.

There are 344 rows and 8 columns within the dataset.
```{r}
  nrow(penguins)
  ncol(penguins)
```

## Calculate the mean flipper length

The mean of flipper length is 200.9152
```{r}
  mean(penguins$flipper_length_mm, na.rm = TRUE)
```

## Graphing
Make a scatter plot of flipper_length_mm (y) vs bill_length_mm (x). Export the first scatterplot to your project directory using ggsave. The plot will be saved to a .pdf file called hwl_plot.png.
```{r}
  ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color=species, na.rm = TRUE)) + geom_point(na.rm = TRUE) + ggtitle("Penguins Flipper Length (mm) vs. Bill Length (mm)")
  ggsave(filename = "hw1_plot.png", height = 4, width = 6)
```




